Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-06-28 paper/main.tex
Paper: Update links to supplementary material

\supplement{Isabelle/HOL Formalization}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
\supplementdetails[cite=CVM_Distinct_Elements-AFP]{Software}{https://isa-afp.org/entries/CVM_Distinct_Elements.html}
\supplementdetails[cite=CVM_Transforms-Github, swhid=swh:1:dir:0d79e265cf5d4d19a0dd1d7e79ed0119cf39ae22]{Software}{https://github.com/joewatt95/CVM/tree/main/isabelle/CVM_Transforms}
\supplementdetails[cite=Negative_Association-AFP]{Software}{https://isa-afp.org/entries/Negative_Association.html}

>>>>

\supplement{Isabelle/HOL Formalization}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
\supplementdetails[cite=CVM_Distinct_Elements-AFP]{Software}{https://isa-afp.org/entries/CVM_Distinct_Elements.html}
\supplementdetails[cite=CVM_Transforms-Github, swhid=swh:1:dir:c677f1e3ced670373c05ac835f1cd342a2777e20]{Software}{https://github.com/joewatt95/CVM/tree/main/isabelle/CVM_Transforms}
\supplementdetails[cite=Negative_Association-AFP]{Software}{https://isa-afp.org/entries/Negative_Association.html}
